### 2011-01-19 htdocs/user.tex
Keyword tags require updating
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1182 40876441-3496-0410-a613-a2fca35b2ae2
Try svn propset svn:keywords "Author Date" user.tex
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1185 40876441-3496-0410-a613-a2fca35b2ae2
Comments on calibration in user.tex
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1228 40876441-3496-0410-a613-a2fca35b2ae2

>>>>

\subsubsection{Hydrodynamic radius}

There is an important issue to understand about the (nominally)
spherical particles in LB. The input radius $a_0$ is used to
construct the link boundary conditions. However, discretisation
errors in the boundary conditions means that the `real' particle
size may be different. This real radius is the hydrodynamic radius $a_h$.
As a further complication, the hydrodynamic radius can also
be a function of viscosity for a given input radius. Some values
are given in Table~X. This values are computed using a calibration
procedure described by Nguyen and Ladd \cite{nguyen2001}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
$\eta$ & \multicolumn{3}{c|}{$a_0$}\\ \cline{2-4} 
       & 1.25 & 2.30 & 4.77 \\
\hline
1/6  & 1.09 (1.05) & 2.23 (2.20) & 4.76 \\
1/100  & 1.40 (1.34) & 2.50 (2.46) & 5.01 \\
1/1000  & 1.63 & 2.71 & 5.23 \\
\hline
\end{tabular}
\end{center}
\caption{A table of calibrated hydrodynamic radii as a function of input
radius and fluid viscosity $\eta$. These figures are for D3Q19 (and D3Q15
in brackets).}
\end{table}

If a calibration is required for a given radius and viscosity,
use the \texttt{calibration on} key pair in the input file. Some
examples are given in the \texttt{tests/calibration} directory.
An apppropriate
number of time steps must be used to allow the system to get over
the initial transient (we use the momentum diffusion time for the
system $L^2/\eta$) and to allow at least one
particle Stokes time ($a/U$). The input radius and hydrodynamic
radius should be set the same in the input file.

% PENDING Ginzburg d'Humieres correct to ghost mode relaxation times
